\ \\ \LARGE\bf Utilization of Reductions and Abstraction Elimination in Typed Genetic Programming

### 2014-01-16 tex/cec14/article.tex
[tex]

% paper title: Must keep \ \\ \LARGE\bf in it to leave enough margin.
\title{\ \\ \LARGE\bf Dodělat název (...)}

@@

\begin{abstract}
Dodělat abstrakt (...)
\end{abstract}
% no key words

>>>>

% paper title: Must keep \ \\ \LARGE\bf in it to leave enough margin.
\title{\ \\ \LARGE\bf 
Utilization of Reductions and Abstraction Elimination in Typed Genetic Programming}

@@

\begin{abstract}
Lambda calculus representation of programs offers a more expressive alternative to traditional S-expressions. In this paper we discuss advantages of this representation coming from use of reductions (beta and eta) and how to overcome disadvantages caused by variables occurring in the programs by use of the abstraction elimination algorithm. We discuss the role of those reductions in the process of generating initial population and compare several crossover approaches including novel approach to crossover operator based both on reductions and abstraction elimination. The design goal of this operator is to turn the disadvantage of abstraction elimination  - possibly quadratic increase of program size - into a virtue; our approach leads to more crossover points. At the same time, utilization of reductions provides offspring of small sizes.
\end{abstract}
% no key words
